Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-02-01 2.background/2.RV_and_RS.tex
all in
I completed the merge of my work on ch. 3, 4 and 5 with the branch "revision-GWAS".  Ready for a "pull" to "revision-GWAS"

More generally, distributions with heavier tails (e.g., log-normal) and lighter tails (e.g., Gompertz) outside the generalized AGG class \eqref{eq:GAGG} may also possess rapidly varying tails;
heavy-tailed distributions like the Pareto and t-distributions, on the other hand, do not.
\stilian{More details on these alternative classes of models can be found in the Supplement.}
{\fbox{Move these to the online Supplement?} 
These alternative classes of models will be introduced when we study the phase transitions in 
Chapter \ref{chap:exact-support-recovery}.}
%For brevity, we focus here on the $\text{AGG}(\nu)$ models.

>>>>

More generally, distributions with heavier tails (e.g., log-normal) and lighter tails (e.g., Gompertz) outside the generalized AGG class \eqref{eq:GAGG} may also possess rapidly varying tails;
heavy-tailed distributions like the Pareto and t-distributions, on the other hand, do not.   More details on these alternative classes of models can be 
found in Chapter \ref{chap:non-AGG}.
